Is essentiality of genes conserved in Enterobacteriaceae?

### 2016-12-06 documents/manuscript.tex
Ran Monte Carlo, edited protein clustering alg
Summed over ii, largest uninterrupted fraction, and monte carlo results

% title goes here:
\begin{flushleft}
{\Large
\textbf\newline{Are essential genes conserved?}
}
\newline
% authors go here:
\\
%Fatemeh Ashari Ghomi\textsuperscript{1},
%Paul P. Gardner\textsuperscript{1,*},
%Lars Barquist\textsuperscript{2}
%\\
%\bigskip
%\bf{1} University of Canterbury
%\\
%\bf{2} Wurzburg University
%\\
%\bigskip
%* paul.gardner@canterbury.ac.nz

@@

% now start line numbers
%\linenumbers

@@

Now that the essentiality of genes can be evaluated using different methods, it is possible to compare the essentiality data in different organisms and investigate the differentiation of essentiality of their genes. Curtis and Brun \cite{curtis_identification_2014} have studied the essentiality changes in cell cycle genes of three alpha-proteobacteria strains: \textit{Caulobacter crescentus}, \textit{Brevundimonas subvibrioides}, and \textit{Agrobacterium tumefaciens} and concluded that although essential genes responsible for cell functions are conserved, there are many essential genes that are specific to each organism. Freed et al.\@ \cite{freed_combining_2016} have investigated the difference between essential genes in \textit{Shigella flexneri} 2a 2457T and \textit{Escherichia coli} K12 BW25113 and shown that some genes have gained essentiality in \textit{Shigella flexneri} while there are no genes that are essential in \textit{Escherichi coli} and not essential in \textit{Shigella flexneri}. Canals et al.\@ \cite{canals_high-throughput_2012} have compared the essentiality of genes in \textit{Salmonella} typhimurium and \textit{Salmonella} Typhi and found that the essentiality of genes differs in different organisms. In a similar study, Barquist et al.\@ \cite{barquist_comparison_2013} have used transposon-directed insertion-site sequencing to study the differentiation of the essentiality of genes in \textit{Salmonella} serovars Typhi and Typhimurium which has led to divergence in their pathogenecity and host ranges. Although there are many studies on differentiation of essentiality in different organisms, these studies usually include two or three strains.

@@

%This defines the bibliographies style. Search online for a list of available styles.
\bibliographystyle{abbrv}

>>>>

% title goes here:
\begin{flushleft}
{\Large
\textbf\newline{Title}
}
\newline
% authors go here:
\\
%Fatemeh Ashari Ghomi\textsuperscript{1},
%Paul P. Gardner\textsuperscript{1,*},
%Lars Barquist\textsuperscript{2}
%\\
%\bigskip
%\bf{1} University of Canterbury
%\\
%\bf{2} Wurzburg University
%\\
%\bigskip
%* paul.gardner@canterbury.ac.nz

@@

% now start line numbers
\linenumbers

@@

Now that the essentiality of genes can be evaluated using different methods, it is possible to compare the essentiality data in different organisms and investigate the differentiation of essentiality of their genes. Curtis and Brun \cite{curtis_identification_2014} have studied the essentiality changes in cell cycle genes of three alpha-proteobacteria strains: \textit{Caulobacter crescentus}, \textit{Brevundimonas subvibrioides}, and \textit{Agrobacterium tumefaciens} and concluded that although essential genes responsible for cell functions are conserved, there are many essential genes that are specific to each organism. Freed et al.\@ \cite{freed_combining_2016} have investigated the difference between essential genes in \textit{Shigella flexneri} 2a 2457T and \textit{Escherichia coli} K12 BW25113 and shown that some genes have gained essentiality in \textit{Shigella flexneri} while there are no genes that are essential in \textit{Escherichi coli} and not essential in \textit{Shigella flexneri}. Canals et al.\@ \cite{canals_high-throughput_2012} have compared the essentiality of genes in \textit{Salmonella} typhimurium and \textit{Salmonella} Typhi and found that the essentiality of genes differs in different organisms. In a similar study, Barquist et al.\@ \cite{barquist_comparison_2013} have used transposon-directed insertion-site sequencing to study the differentiation of the essentiality of genes and ncRNAs in \textit{Salmonella} serovars Typhi and Typhimurium. Although there are many studies on differentiation of essentiality in different organisms, these studies usually include two or three strains.

@@

%This defines the bibliographies style. Search online for a list of available styles.
\bibliographystyle{apalike}
